A quantitative framework for investigating the reliability of empirical network construction: supplemental information

### 2018-06-27 manuscript/CI_interactions.tex
Think I just need to fine-tune that figureg

    Note that $\lambda$ is not a single point estimate but rather a random variable with an unknown distribution. This means that if $k = 0$ in a given sample, this does not necessarily imply that the two species will never interact. Rather, $k = 0$ implies that `no interaction' is the most likely outcome when the species do co-occur but there is nonetheless some chance that the two species \emph{could} interact. In the situation where $k>0$, in contrast, we are sure that the interaction is feasible ($L = 1$). If $n>k>0$, the interaction is feasible but there may be local constraints ($X = 0$) or detection errors ($D<1$) causing the interaction not to be observed in some samples.

@@

      When using an informative prior, it is important to ensure that this prior accurately reflects the focal  system. For example, if the focal system is a large network containing many plant species and insects from different families, it is inappropriate to use a prior distribution drawn from a small network describing interactions between different genotypes of a single plant species with a set of closely-related insects. The similarity of traits across genotypes within a species means that an insect which interacts with one genotype is likely to interact with many others. Trait differences between species mean that a species-species network will likely contain fewer interactions than a genotype-species network. Similarly, highly-aggregated networks containing nodes which represent whole classes or families are likely to have very different structures than networks where most nodes represent single species as aggregated nodes are likely to have more interaction partners than single species.

      The choice of prior will depend on the information available. In general, it is best to use a prior taken from a similar system as emphasized above. If such data are not available, a prior based on many networks systems with a similar level of resolution could be useful, as could a prior based on a preliminary round of sampling (analogous to ``training data"). If there is no suitable informative prior, it is best to use an explicitly uninformative prior. While an uninformative prior will not greatly reduce variance about $\lambda$, it does clearly state our lack of prior knowledge and will not bias our conclusions.

@@

      To illustrate the process of constructing a Bayesian network, we use the well-sampled system of willow (\emph{Salix}) species, herbivorous gallers, and their natural enemies described by~\citet{Kopelke2017}. This dataset consists of a single community type sampled across Europe over 29 years and at 374 unique locations. The data were collected over 29 years at 374 unique locations across Europe. The meta-network consists of 1,173 different interactions between 52 \emph{Salix} nodes, 92 herbivore nodes, and 126 natural enemy nodes (see \emph{Appendix S3} for details).

      The high spatiotemporal resolution and unusally high sampling effort of this dataset make it particularly well suited for illustrating the difficulties in completely sampling a network. To show the gaps in sampling, we compared the frequencies of observed co-occurrences and interactions. We analysed both the \emph{Salix}-galler and galler-natural enemy components of the network but, for brevity, present only the latter here (see~\emph{Appendix S4} for \emph{Salix}-galler results).

@@

        To obtain priors based on a single sub-network --Zillis in Graub\"{u}nchen, Switzerland-- we estimated frequencies of interactions based on the normalised degree of each species in each network component (see \emph{Appendix S6} for details and code). Using these prior parameters, we then estimated the posterior distributions of interaction probabilities $\lambda$. For species without observed interactions ($n = 0$), the posterior distribution is identical to the prior distribution. For species where $n>0$, we can update the prior distribution with data. If we consider only pairs of species which were observed to co-occur but not to interact, $k_{ij}$ is always 0 and only $n_{ij}$ will vary between species pairs. This gives $\alpha'$=$\alpha$ and $\beta'$=$\beta + n_{ij}$. We calculated posterior distributions and 95\% credible intervals (see function ``credible\_interval";~\emph{Appendix S7}) for species with $n$ ranging between 0 and 374, the total number of sites in our dataset.

@@

      Researchers usually use interaction matrices as a tool to calculate measures of network structure. Computing most network metrics is straightforward when the different $\lambda$ of the adjacency matrix are known and assumed not to vary~\citep{Poisot2016}. Incorporating variance in $\lambda$ into these calculations, however, is not so easy. Computation of these metrics involves non-linear functions. By Jensen's inequality~\citep{Jensen1906}, this means that the average of a network metric (a function of stochastic interactions) is not the same as the network metric calculated based on the average interaction probability. Any uncertainty in the values of $\lambda$ could bias both the mean and variance of network metrics, giving misleading results. One way to avoid this situation is to calculate the properties of a suite of simulated networks.

@@

  Most pairs of species (9,794/12,096 galler-natural enemy pairs) were never found co-occurring and, for species that did occur together, the total number of co-occurrences was generally low (mean=3.87; Fig.~\ref{histograms}A). The bulk of these co-occurring species pairs were never observed to interact: only 7.76\% of galler-natural enemy pairs were observed interacting. Of those pairs that did interact, the incidence of interaction was also low (mean=4.04; Fig.~\ref{histograms}B) and tended to be lower than the number of observed co-occurrences (Fig.~\ref{histograms}C).

@@

  For most pairs of species $i$ and $j$, however, $n_{ij}$ was much less than 374 and our posterior mean and variance therefore retain more of the influence of the prior. We can see this in the increasing means and variances as we decrease $n_{ij}$ (Fig.~\ref{Salix_pdfs_cdfs};~\emph{Appendix S8}). The number of samples required to be 95\% confident that the interaction probability between galler and natural enemy species is below a threshold increases quickly as the threshold decreases (Fig.~\ref{Salix_pdfs_cdfs};~\emph{Appendix S8}). To be 95\% confident that the probability of interaction is below 0.1, 0.05, or 0.01 would require 15, 39, and 229 observed co-occurrences, respectively. Note that these are relatively large sample sizes compared to currently-available empirical networks~\citep{Morris2014}.

  Scaling up to network structure, we found that the connectance, mean links per galler, and mean links per natural enemy were much lower in the observed web (C=0.078, $L_{galler}$=9.99, and $L_{natural enemy}$=7.45, respectively) than in the posterior webs (0.186 $\leq$ C $\leq$ 0.198, 13.4 $\leq L_{galler} \leq$ 14.6, and 23.4 $\leq L_{natural enemy} \leq$ 25.0). When the detection probability was relatively low (i.e., 50\%), however, the properties of randomised networks became similar to those in the observed webs (Fig.~\ref{posterior_webs}A,B,D). Nestedness was higher in the observed network (NODF=6.85) than in the posterior webs (6.31 $\leq NODF \leq$ 6.82; Fig.~\ref{posterior_webs}C); in this case, the stronger the detection filter, the farther apart were the observed and posterior webs. In general, the observed network is most similar to simulated networks where only half of the plausible links are detected.

@@

  Real interaction networks vary over several dimensions~\citep{Kitching1987,Olesen2011a,Pires2011a,Baiser2012,Fodrie2015,Novak2015}, leading to pervasive under-estimation of interactions in published networks. Even in the most extensive data set that we could find, there was very little empirical data for each species pair. Most pairs of species were not observed co-occurring even once, less than 10\% of species pairs were observed interacting, and no pairs were observed to co-occur frequently enough to reach the threshold for an interaction probability of 0.01. This suggests that limited sampling is a major source of uncertainty in empirical networks. This dataset also illustrates the problem of process uncertainty - pairs of species which were observed to interact did not interact in all of the samples in which they co-occurred. As such, increasing sampling is likely to add more zeros than ones to an interaction network.

  Using prior knowledge to build a Bayesian distribution for each interaction probability allows us to set appropriate bounds on interaction probabilities for species which were rarely or never observed co-occurring. In such cases, an informative prior distribution gives us more reasonable estimates of interacition probabilities than assuming that no unobserved interactions can ever occur. This approach will also be useful when considering interactions involving species entering new ranges due to climate change or introductions. Understanding these species' interactions is important for a variety of conservation questions, and a Bayesian approach using a trait-matching model or data from species' current ranges could help us to anticipate how species will integrate into new communities.

@@

  Based on the framework described above, we can now offer some recommendations for improved descriptions of ecological interactions. First, sample sizes should be as large as possible in order to reduce detection uncertainty. Second, where sampling on the order of 30-50 observations per species pair is not possible (i.e., in most cases), researchers should acknowledge the varying levels of confidence surrounding interactions between different species pairs. Including the $n$ and $k$ values for each interaction will clearly indicate which unobserved interactions are most likely to be observed with further sampling and which estimates are more reliable. Third, the uncertainty around interactions should be incorporated in calculations of network properties. Re-sampling networks based on a probabilistic understanding of networks is straightforward and gives distributions for network properties rather than point estimates. This not only acknowledges the fact that interactions vary over time and space but will also facilitate comparisons between networks by adding confidence intervals to estimates of network properties. This will allow us to say whether networks have different structures \emph{and} whether those differences are greater than we would expect given the inherent variability of interactions. To facilitate the practical application of these recommendations, we provide all code used in this paper in the supplementary material.

@@

  \begin{figure}[h!]
    \caption{Three nested levels of uncertainty mean that an observed interaction matrix is unlikely to capture all of the interactions that can really occur at a site. Beginning with a true interaction matrix (top left) of zeros (interactions that cannot occur, white) and ones (interactions that do occur, black), each level of uncertainty adds more zeros. Interaction uncertainty refers to the fact that some interactions are more likely than others based on species' traits. For example, lions are less likely to predate upon elephants than zebras. If our trait model is incomplete (e.g., if we neglect group hunting in lions), we might assume that elephants are too large to ever be prey for lions. Process uncertainty further reduces the probability of observing an interaction as not every interaction occurs during each sampling period. We show six example interaction matrices representing interactions observed over two days at three sites. The probability of observing an interaction now reflects the rarity of each interaction occurring during a given sampling day. Detection uncertainty reflects the fact that not all interactions are equally detectable. For example, rare species may be hard to find and follow in the field. After applying these three layers of uncertainty, some of the interactions which truly occur are very unlikely to be observed. An observed matrix sampled based on this matrix (lower left) is likely to contain far fewer interactions than the original, true matrix.}
    \label{conceptual_fig}
    \begin{center}
    \includegraphics*[height=.6\textheight]{figures/conceptual_fig.eps}
    \end{center}
    \end{figure}

  \begin{figure}[h!]
      \caption{Despite the replication in our empirical dataset, most galler-natural enemy pairs were never observed co-occurring and those that did co-occur rarely interacted. \textbf{A)} Here we show a histogram of the number of pairs of species observed co-occurring at least once. 9794 galler-enemy pairs were never observed co-occurring (not shown).
      \textbf{B)} Here we show a histogram of the number of observed interactions within pairs of co-occurring species. Species which co-occurred but never interacted are included. 
      \textbf{C)} Here we show, for each species pair, the number of observed interactions plotted against the number of observed co-occurrences. The red, dashed line indicates a 1:1 relationship between interactions and co-occurrences.}
      \label{histograms}
      \begin{center}
      \includegraphics*[height=.6\textheight]{figures/GP_histogram.eps}
      \end{center}
      \end{figure}

  \begin{figure}[h!]
    \caption{Imperfect detection of interactions increases the number of samples required to be confident that an interaction does not occur. Assume that two species cannot interact (i.e., $\lambda=0$) and that the number of observed interactions follows a binomial distribution. Here we show the upper bound (solid black line) of a 95\% Cloper-Pearson true credible interval for the interaction probability $\lambda$ for a pair of species that has been observed co-occurring $n$ times but never interacting ($k = 0$). The upper limit of the credible interval only reaches 0.1 (dashed, red line) with 35 observations. Thus, adding more observations is useful in controlling uncertainty, but the number of observations added must be very high. }
    \label{upper_limits}
    \begin{center}
    \includegraphics*[width=.8\textwidth]{figures/upper_limit_DG.eps}
    \end{center}
    \end{figure}

  \begin{figure}[h!]
    \caption{Using prior distributions based on a single site (Zillis in Graub\"{u}nden, Switzerland) from~\citet{Kopelke2017}, we calculate posterior distributions for the probability of interaction ($\lambda$) between two species that have not yet been observed interacting ($k = 0$). 
    Posterior distributions (curves) and 95\% credible intervals (lines at top of panell) for $\lambda$ narrow and approach zero as the number of observed co-occurrences ($n$) increases. Diamonds indicate the maximum likelihood estimator for the mean probability of interaction.
    Dashed lines indicate threshold probabilities of 0.01, 0.05, and 0.1. The number of samples required to obtain a 95\% credible interval below each threshold increases rapidly. It takes just over 20 observed co-occurrences to be 95\% confident that $\lambda<0.10$, approximately 50 co-occurrences to be 95\% confident that $\lambda<0.05$, and over 100 co-occurrences to be 95\% confident that $\lambda<0.01$.}
    \label{Salix_pdfs_cdfs}
    \begin{center}
    \includegraphics*[width=.8\textwidth]{figures/GP_pdfs_increasing_N_Zillis.eps}
    \end{center}
    \end{figure}

@@

  \begin{figure}[h!]
    \caption{Mean connectance, links per galler, nestedness (NODF), and links per natural enemy for networks assembled using posterior distributions based on a single site (Zillis in Graub\"{u}nden, Switzerland) from~\citet{Kopelke2017} occupied a narrow range. To obtain distributions of network properties, we created 100 ``posterior-sampling" networks and then, for each of these, created 100 ``detection-filter" networks by randomly sampling 50\%-99\% of the interactions included in the posterior-sampling network. This simulates imperfect detection of interactions in the field. Each point represents the mean (+/- SD) network property (e.g., connectance) obtained from a set of 100 detection-filter networks. The detection-filter networks cover a broader range of network properties than the posterior-sampling networks but the value of each property decreases as the strength of the detection filter increases. Values in the original web are indicated by dashed lines.}
    \label{posterior_webs}    
    \begin{center}
    \includegraphics[width=.8\textwidth]{figures/GP_posterior_properties_Zillis.eps}
    \end{center}
    \end{figure}

>>>>

    Note that $\lambda$ is not a point estimate but rather a random variable with an unknown distribution. This means that if $k = 0$ in a given sample, this does not necessarily imply that the two species will never interact. Rather, $k = 0$ implies that `no interaction' is the most likely outcome when the species do co-occur but there is nonetheless some chance that the two species \emph{could} interact. In the situation where $k>0$, in contrast, we are sure that the interaction is feasible ($L = 1$). If $n>k>0$, the interaction is feasible but there may be local constraints ($X = 0$) or detection errors ($D<1$) causing the interaction not to be observed in some samples.

@@

      It is important to ensure that an informative prior accurately reflects the focal  system. For example, if the system is a large network containing many plant species and insects from different families, it is inappropriate to use a prior distribution drawn from a small network describing interactions between different genotypes of a single plant species and a set of closely-related insects. The similarity of traits across genotypes within a species means that an insect which interacts with one genotype is likely to interact with many others. Trait differences between species mean that a species-species network will likely contain fewer interactions than a genotype-species network. Similarly, highly-aggregated networks containing nodes which represent whole classes or families are likely to have very different structures than networks where most nodes represent single species as aggregated nodes are likely to have more interaction partners than single species.

      The choice of prior will depend on the information available. In general, it is best to use a prior taken from a similar system as emphasized above. If such data are not available, a prior based on many networks with a similar level of resolution could be useful, as could a prior based on a preliminary round of sampling (analogous to ``training data"). If there is no suitable informative prior, it is best to use an explicitly uninformative prior. While an uninformative prior will not greatly reduce variance about $\lambda$, it does clearly state our lack of prior knowledge and will not bias our conclusions.

@@

      To illustrate the process of constructing a Bayesian network, we use the well-sampled system of willows (\emph{Salix}), herbivorous gallers, and their natural enemies described by~\citet{Kopelke2017}. This dataset consists of a single community type sampled across Europe over 29 years and at 374 unique locations. The data were collected over 29 years at 374 unique locations across Europe. The meta-network consists of 1,173 different interactions between 52 \emph{Salix} nodes, 92 herbivore nodes, and 126 natural enemy nodes (see \emph{Appendix S3} for details).

      The high spatiotemporal resolution and unusally high sampling effort of this dataset make it well suited for illustrating the difficulties in completely sampling a network. To show the gaps in sampling, we compared the frequencies of observed co-occurrences and interactions. We analysed both the \emph{Salix}-galler and galler-natural enemy components of the network but, for brevity, present only the latter here (see~\emph{Appendix S4} for \emph{Salix}-galler results).

@@

        To obtain priors based on a single sub-network --Zillis in Graub\"{u}nchen, Switzerland-- we estimated frequencies of interactions based on the normalised degree of each species in each network component (see \emph{Appendix S6} for details and code). Using these prior parameters, we then estimated the posterior distributions of interaction probabilities $\lambda$. For species without observed interactions ($n = 0$), the posterior distribution is identical to the prior distribution. For species where $n>0$, we can update the prior distribution with data. If we consider only pairs of species which were observed co-occurring but not interacting, $k_{ij}$ is always 0 and only $n_{ij}$ will vary between species pairs. This gives $\alpha'$=$\alpha$ and $\beta'$=$\beta + n_{ij}$. We calculated posterior distributions and 95\% credible intervals (see function ``credible\_interval";~\emph{Appendix S7}) for species with $n$ ranging between 0 and 374, the total number of sites in our dataset.

@@

      Researchers usually use interaction matrices as a tool to calculate measures of network structure. Computing most network metrics is straightforward when the different $\lambda$ of the adjacency matrix are known and assumed not to vary~\citep{Poisot2016}. Incorporating variance in $\lambda$ into these calculations, however, is not so easy. Computation of these metrics involves non-linear functions. By Jensen's inequality~\citep{Jensen1906}, this means that the average of a network metric (a function of stochastic interactions) is not the same as the network metric calculated based on the average interaction probability. Any uncertainty in the values of $\lambda$ could bias both the mean and variance of network metrics, giving misleading results (simulated in \emph{Appendix S8}). One way to avoid this situation is to calculate the properties of a suite of simulated networks.

@@

  Most pairs of species (9,794/12,096) never co-occurred and, for species that did occur together, the total number of co-occurrences was generally low (mean=3.87; Fig.~\ref{histograms}A). The bulk (92.24\%) of these co-occurring species pairs were never observed interacting. Of those pairs that did interact, the incidence of interaction was also low (mean=4.04; Fig.~\ref{histograms}B) and was lower than the number of observed co-occurrences (Fig.~\ref{histograms}C).

@@

  For most pairs of species $i$ and $j$, $n_{ij}$ was much less than 374 and our posterior mean and variance therefore retain more of the influence of the prior. We can see this in the increasing means and variances as we decrease $n_{ij}$ (Fig.~\ref{Salix_pdfs_cdfs};~\emph{Appendix S9}). To be 95\% confident that the probability of interaction is below 0.1, 0.05, or 0.01 would require 15, 39, and 229 observed co-occurrences, respectively. Note that these are relatively large sample sizes compared to currently-available empirical networks~\citep{Morris2014}.

  Scaling up to network structure, we found that the connectance and mean links per galler and natural enemy were much lower in the observed web (C=0.078, $L_{galler}$=9.99, and $L_{natural enemy}$=7.45, respectively) than in the posterior webs (0.186 $\leq$ C $\leq$ 0.198, 13.4 $\leq L_{galler} \leq$ 14.6, and 23.4 $\leq L_{natural enemy} \leq$ 25.0). When the detection probability was relatively low (i.e., 50\%), however, the properties of randomised networks became similar to those in the observed webs (Fig.~\ref{posterior_webs}A,B,D). Nestedness was higher in the observed network (NODF=6.85) than in the posterior webs (6.31 $\leq NODF \leq$ 6.82; Fig.~\ref{posterior_webs}C); in this case, the stronger the detection filter, the farther apart were the observed and posterior webs. In general, the observed network is most similar to simulated networks where only half of the plausible links are detected.

@@

  Real interaction networks vary over several dimensions~\citep{Kitching1987,Olesen2011a,Pires2011a,Baiser2012,Fodrie2015,Novak2015}, leading to pervasive under-estimation of interactions in published networks. Even in the most extensive data set that we could find, there was very little empirical data for each species pair. Most pairs of species were not observed co-occurring even once, less than 10\% of species pairs were observed interacting, and no pairs were observed to co-occur frequently enough to conclude that their probability of interacting was below 0.01. This suggests that limited sampling is a major source of uncertainty in empirical networks. This dataset also illustrates the problem of process uncertainty - pairs of species which were observed interacting did not interact in all of the samples in which they co-occurred. Increasing sampling is therefore likely to add more zeros than ones to an interaction network.

  Using prior knowledge to build a Bayesian distribution for each interaction probability allows us to set appropriate bounds on interaction probabilities for species which were rarely or never observed co-occurring. In such cases, an informative prior distribution gives us more reasonable estimates of interaction probabilities than assuming that $p$=0 for unobserved interactions. This approach is particularly useful when considering interactions involving species entering new ranges due to climate change or introductions. Understanding these species' interactions is important for a variety of conservation questions, and a Bayesian approach using a trait-matching model or data from species' current ranges could help us to anticipate how species will integrate into new communities.

@@

  Based on the framework described above, we can now offer some recommendations for improved descriptions of ecological interactions. First, sample sizes should be as large as possible in order to reduce detection uncertainty. Second, where sampling on the order of 30-50 observations per species pair is not possible (i.e., in most cases), researchers should acknowledge the varying levels of confidence surrounding interactions between different species pairs. Including the $n$ and $k$ values for each interaction will clearly indicate which unobserved interactions are most likely to be observed with further sampling and which estimates are more reliable. Third, the uncertainty around interactions should be incorporated in calculations of network properties. Re-sampling networks based on a probabilistic understanding of networks is straightforward and gives distributions for network properties rather than point estimates. This not only acknowledges the fact that interactions vary over time and space but will also facilitate comparisons between networks by adding confidence intervals to ezostimates of network properties. This will allow us to say whether networks have different structures \emph{and} whether those differences are greater than we would expect given the inherent variability of interactions. To facilitate the practical application of these recommendations, we provide all code used in this paper in the supplementary material.

@@

  \begin{figure}[h!]
    \caption{Three nested levels of uncertainty mean that an observed interaction matrix is unlikely to capture all of the interactions that can really occur at a site. Interaction uncertainty means that some inteactions that truly occur (black squares in True matrix) are less likely than others (grey squares) based on species traits. For example, lions are less likely to predate upon elephants than zebras. If our trait model is incomplete (e.g., if we neglect group hunting in lions), we might assume that elephants are too large to ever be prey for lions and assign this interaction a probability of 0.\\
    Process uncertainty describes the fact that interactions occur with different probabilities during any given sample. We show six example networks representing interactions observed over two days at three sites. Interactions which occur during fewer sampling days are less likely to be observed.\\
    Detection uncertainty reflects the fact that not all interactions are equally detectable. For example, interactions involving cryptic species are less likely to be seen.\\
    After applying these three layers of uncertainty, some interactions which truly occur are very unlikely to be observed. An observed matrix sampled based on this matrix (lower left) is thus likely to contain far fewer interactions than the original, true matrix.}
    \label{conceptual_fig}
    \begin{center}
    % \includegraphics*[height=.5\textheight]{figures/conceptual_fig.eps}
    \end{center}
    \end{figure}

  \begin{figure}[h!]
      \caption{Despite the replication in our empirical dataset, most galler-natural enemy pairs were never observed co-occurring and those that did co-occur rarely interacted. \textbf{A)} Here we show a histogram of the number of pairs of species observed co-occurring at least once. 9794 galler-enemy pairs were never observed co-occurring (not shown).
      \textbf{B)} Here we show a histogram of the number of observed interactions within pairs of co-occurring species. Species which co-occurred but never interacted are included. 
      \textbf{C)} Here we show, for each species pair, the number of observed interactions plotted against the number of observed co-occurrences. The red, dashed line indicates a 1:1 relationship between interactions and co-occurrences.}
      \label{histograms}
      \begin{center}
      % \includegraphics*[height=.6\textheight]{figures/GP_histogram.eps}
      \end{center}
      \end{figure}

  \begin{figure}[h!]
    \caption{Imperfect detection of interactions increases the number of samples required to be confident that an interaction never occurs. Assume that two species cannot interact (i.e., $\lambda=0$) and that the number of observed interactions follows a binomial distribution. Here we show the upper bound (solid black line) of a 95\% Cloper-Pearson true credible interval for the interaction probability $\lambda$ for a pair of species that has been observed co-occurring $n$ times but never interacting ($k = 0$). The upper limit of the credible interval only reaches 0.1 (dashed, red line) with 35 observations. Thus, adding more observations is useful in controlling uncertainty, but the number of observations added must be very high. }
    \label{upper_limits}
    \begin{center}
    % \includegraphics*[width=.8\textwidth]{figures/upper_limit_DG.eps}
    \end{center}
    \end{figure}

  \begin{figure}[h!]
    \caption{Using prior distributions based on a single site (Zillis in Graub\"{u}nden, Switzerland) from~\citet{Kopelke2017}, we calculate posterior distributions for the probability of interaction ($\lambda$) between two species that have not yet been observed interacting ($k = 0$). 
    Posterior distributions (curves) and 95\% credible intervals (lines at top of panell) for $\lambda$ narrow and approach zero as the number of observed co-occurrences ($n$) increases. Diamonds indicate the maximum likelihood estimator for the mean probability of interaction.
    Dashed lines indicate threshold probabilities of 0.01, 0.05, and 0.1. The number of samples required to obtain a 95\% credible interval below each threshold increases rapidly. It takes just over 20 observed co-occurrences to be 95\% confident that $\lambda<0.10$, approximately 50 co-occurrences to be 95\% confident that $\lambda<0.05$, and over 100 co-occurrences to be 95\% confident that $\lambda<0.01$.}
    \label{Salix_pdfs_cdfs}
    \begin{center}
    % \includegraphics*[width=.8\textwidth]{figures/GP_pdfs_increasing_N_Zillis.eps}
    \end{center}
    \end{figure}

@@

  \begin{figure}[h!]
    \caption{Mean connectance, links per galler, nestedness (NODF), and links per natural enemy for networks assembled using posterior distributions based on a single site (Zillis in Graub\"{u}nden, Switzerland) from~\citet{Kopelke2017} occupied a narrow range. To obtain distributions of network properties, we created 100 ``posterior-sampling" networks and then, for each of these, created 100 ``detection-filter" networks by randomly sampling 50\%-99\% of the interactions included in the posterior-sampling network. This simulates imperfect detection of interactions in the field. Each point represents the mean (+/- SD) network property (e.g., connectance) obtained from a set of 100 detection-filter networks. The detection-filter networks cover a broader range of network properties than the posterior-sampling networks but the value of each property decreases as the strength of the detection filter increases. Values in the original web are indicated by dashed lines.}
    \label{posterior_webs}    
    \begin{center}
    % \includegraphics[width=.8\textwidth]{figures/GP_posterior_properties_Zillis.eps}
    \end{center}
    \end{figure}

### 2018-06-27 manuscript/supplemental.tex
Think I just need to fine-tune that figureg

\section*{Appendix S8: Calculating the credible interval around a probability estimate}

>>>>

\section*{Appendix S8: Simulating the effects of uncertainty on network structure}

  To demonstrate the effects of nested interaction, process, and detection uncertainty on network structure, we can observe how the structure of randomly-generated networks changes as we add layers of uncertainty. We began by constructing 100 "true" networks with 50 plant species, 50 galler species, and a connectance of 0.1. We ensured that each network had at least one link per plant and per galler. For each network, we calculated the mean number of links per plant, mean number of links per galler, and nestedness (NODF) as described in the main text. For simplicity, we assume that there is no interaction uncertainty in this system (i.e., all interactions are either 100\% feasible or 100\% infeasible based on species' traits).

  Taking each "true" network as a starting point, we then applied process uncertainty. The probability $p$ of the occurrance of each interaction on a given sampling day was assigned a random probability drawn from the uniform distribution. As the probability that an interaction will occur during sampling also depends on the probability of the two species co-occurring, we also assigned a random number of sampling days on which each species co-occurred. The number of co-occurrances, $n$, was drawn from a uniform distribution and could be any integer between 0 and 30 (our simulated number of sampling days), inclusive. The number of occurrances, $k$, of each interaction was then drawn from a binomial distribution based on $n$ and $p$. If the number of occurrances during sampling was greater than 0 and the interaction occurred in the true network, we included the interaction in the "process-filtered" network. As the inclusion of interactions in the process matrices is random, we created 100 process-filtered networks for each true network. For each network, we calculated the number of plants and gallers (after removing any species with no interactions), mean links per plant and per galler, connectance, and NODF.

  Next, we applied a layer of detection uncertainty to create "detection-filtered" networks. As with the process-filtered networks, we randomly selected the number of times each species co-occurred, $n$, from a uniform distribution. We also randomly selected the probability, $p$, of detecting each interaction. To reflect the fact that some interactions are easy to observe but many will be more difficult (because one or both interaction partners are rare, cryptic, or difficult to rear in the lab), we drew $p$ from a beta distribution with shape parameters 2 and 10. We created 100 detection-filtered networks for each process-filtered network (10000 per true network). For each network, we calculated the number of plants and gallers (after removing any species with no interactions), mean links per plant and per galler, connectance, and NODF. Code used in this simulation example is contained in the file \emph{simulation_example.R}, uploaded separately.

  With each additional layer of uncertainty, the number of plants and gallers included in the web decreased (state means here). The connectance and number of links per plant and per galler decreased significantly at each level (Fig.~\ref{sim_props}A,B,D). The effects of uncertainty on nestedness were less predictable. The process-filtered networks were significantly less nested than the original networks, but the variation in the detection-filtered webs was so great that there were no significant differences between the original and detection-filtered networks (Fig.~\ref{sim_props}C). This simulation demonstrates the fact that process and detection uncertainty mean that we are very unlikely to observe all of the interactions that can truly occur in a system, as well as the sometimes unpredictable effects this uncertainty can have on higher-order structures such as nestedness.

  Note that this simulation uses several simplifying assumptions. For instance, we treat interactions as independent and ignore the possibility for, for example, competition between gallers. A thorough exploration of the effects of interaction contingency, different distributions of co-occurrences, etc. would be an interesting topic for future work but is beyond the scope of the current study. We also neglect interaction uncertainty in this example. Interaction uncertainty could be included by, for example, modelling interactions between individuals of each species. In this framework, individuals could vary in some trait (e.g., body size) that affects the interactions in which they participate. Very small or very large individuals might not participate in some interactions that are feasbile for most members of the species.

  \begin{figure}
  \label{sim_props}
  \caption{We created 100 random networks containing 50 plants and 50 gallers, with a connectance of 0.1. For each of these "original" networks, we created 100 process-filtered ("process") networks incorporating uncertainty around the occurrance of each interaction during sampling. For each "process" network, we further created 100 detection-filtered ("detection") networks incorporating uncertainty around the detection of each interaction. For each network, we show the mean (+/- SD) connectance, links per plant, nestedness (NODF), and links per galler.}
  \begin{center}
  \includegraphics*[width=\textwidth]{figures/simulation_example.eps}
  \end{center}
  \end{figure}

\section*{Appendix S9: Calculating the credible interval around a probability estimate}
